Summary

### 2015-10-29 inst/examples/summary.Rmd
separated functions into their own files and removed empty roxygen lines to avoid some warnings in official build check

[Successfully converted publication times](publication-time-accepted.csv)

[Discarded publication times](publication-time-discarded.csv)

@@

```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
df$author <- paste(df$family_name,df$first_name,sep=", ")
ntop <- 50
a <- rev(rev(sort(table(df$author)))[2:ntop+1])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

@@

```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}

# List all topics
spl <- strsplit(na.omit(as.character(df$subject_topic)), ";")

@@

```{r geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

>>>>

[Successfully converted publication times](output.tables/publication-time-accepted.csv)

[Discarded publication times](output.tables/publication-time-discarded.csv)

@@

```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
a <- rev(rev(sort(table(df$author)))[2:ntop+1])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

@@

```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
# List all topics
spl <- strsplit(na.omit(as.character(df$subject_topic)), ";")

@@

```{r geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```
